---
title: "Saving PNG Images"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Saving PNG Images}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

ChemSpider's API services offers the functionality to download image files of the chemicals. This functionality is implemented in the `get_record_id_image()` function. These image files can also be stored straight from R. Here we demonstrate the functionality with the 


## Installing the required `{magick}` and `{png}` packages

Before downloading an example image for caffeine, the `{magick}` and `{png}` packages needs to be installed.
```{r,eval=FALSE}
install.packages(c("magick", "png"))
```


## Downloading the PNG image of caffeine

First, the `chemspiderapi` package needs to be loaded and the API key needs to be retrieved.
```{r,eval=FALSE}
library(chemspiderapi)

apikey <- keyring::key_get(service = "ChemSpider API key", username = Sys.getenv("USERNAME"))
```

Now, the "raw" image file (ChemSpider ID 2424) is downloaded using `get_record_id_image()`. The raw image is then decoded using the `jsonlite::base64_dec()` function. 
```{r,eval=FALSE}
caffeine_image_raw <- get_record_id_image(record_id = 2424L, apikey = apikey)

library(jsonlite)

caffeine_image <- base64_dec(caffeine_image_raw$image)
```

### Saving the image using the `{magick}` package

The decoded image needs to be read in using the `magick::image_read()` functionality.
```{r,eval=FALSE}
library(magick)

caffeine_png <- image_read(caffeine_image)
```

The loaded image can be viewed by calling the object. 
```{r,eval=FALSE}
caffeine_png
```

Saving the image is possible using the `magick::image_write()` function.
```{r,eval=FALSE}
image_write(caffeine_png, path = "caffeine.png")
```

### Saving the image using the `{png}` package

The decoded image needs to be read in using the `png::readPNG()` functionality.
```{r,eval=FALSE}
library(png)

caffeine_png <- readPNG(caffeine_image)
```

Saving the image is possible using the `png::writePNG()` function.
```{r,eval=FALSE}
writePNG(caffeine_png, target = "caffeine.png")
```
